Innovation and elaboration on the avian tree of life - supplementary materials

### 2022-09-09 Manuscript/supplementaries.tex
Update supplementaries.tex

\begin{tabular}{llll}

@@

clade's major axis          & the \textbf{line of least resistance} specific to a clade & the first \textbf{eigenvector} of a \textbf{clade}'s \textbf{variance-covariance} matrix &  \\ 

>>>>

\begin{tabular}{p{0.2\textwidth}p{0.4\textwidth}p{0.4\textwidth}}

@@

clade's major axis          & the \textbf{line of least resistance} specific to a clade & the first \textbf{eigenvector} of a \textbf{clade}'s \textbf{variance-covariance} matrix \\ 
